---
title: "Traveler.Experience.Pt2.v1"
author: "Planning & Regional Development"
date: "12/4/2019"
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=FALSE)
```

\pagenumbering{arabic} 

#Part 2. 

WORK THIS OUT IN cx2scratch and bring over here when finished. 







```{r}
setwd("~/Dropbox/Work and research/Port Authority/cx2") 
library(readxl) 
library(mice) 
library(dplyr) 
library(Hmisc) 
library(imputeMissings) 
library(ggplot2) 
library(beepr) 
library(ggdendro) 
library(reshape2) 
library(tidyr) 
library(remotes) 
#remotes::install_github("njtierney/naniar") 
library(naniar) 
library(tidyverse) 
library(tree) 
library(rpart) 

rm(list = ls()) # clear global environment 
cat("\014") # clear the console 
options(warn=-1) # suppress annoying warnings 
```

```{r, echo=FALSE}
pmiss = function(x){sum(is.na(x))/length(x)*100} 
```


The ASQ data from ACI is relatively clean. 
```{r}
asq193 = read_excel("./ACI - ASQ/2019 Q3/ACI ASQ Survey Main_ Q3 2019 Data-EXCEL-v1.xlsx")
asq193 = as.data.frame(asq193) 
names(asq193) = tolower(names(asq193)) 
```

The JD Power data (minus variables with significant missing observations) has been cleaned in Part 1. 

```{r}
jdp18 = read.csv("./JDPower18_noNA.csv") 
```

There are obvious patterns in that sample: 

```{r, include=TRUE, fig.width=8, fig.height=10}
gg_miss_var(asq193, show_pct=TRUE)
```

```{r, echo=TRUE, include=FALSE}
head(apply(asq193,2,pmiss),15)
```

Overall, roughly half of the data is missing. And it definitely isn't missing at random. Some variables are missing no observation. Many are missing around 20 percent - and that number looks very consistant across that group of variables. Then the share of missing observations increases. This continues all the way up until a collection of variables show no actual measurements - all observations there are missing. 

```{r, include=TRUE, fig.width=8, fig.height=10}
vis_miss(asq193)
```

So we can evaluate NAs further or we can limit the data set to everything missing no more than that much data, then do some strategic selection or imputation and move forward. 

A few potential next steps, in order: 

1. Identify variables with no (or practically no) missing observations and review the list. 
2. Repeat, but including variables up to the 21 percent missing observation shelf. 
3. Consider using subset #1 or #2 for some predictive work. 
4. Perform #3 again but using ASQ data. 
5. Compare top predictors across each data set. Anything interesting or surprising? 

We've taken step 1 below. 

###1. Variables (JD Power) with no NAs. 
```{r}
share.Na = as.data.frame(t(jd18.2 %>% 
   summarise_each(funs(100*mean(is.na(.)))))) 
```

There are 40 variables without missing values: 
```{r, include=TRUE, echo=FALSE} 
short = subset(share.Na, share.Na==0) 
names(short) = c("Share.NA") 
short 
short = jd18.2[ , colSums(is.na(jd18.2)) == 0] 

```


#Tree 
```{r}
summary(short$Overall.Satisfaction.Index) 
short$high = ifelse(short$Overall.Satisfaction.Index <= 765,"No","Yes") 
#jd18.tree = sapply(jd18,function(x) as.numeric(as.character(x))) 
#tree.jd18 = tree(high ~., data=jd18.tree) 

rm(nombres) 
sort(names(jd18)) 
jd18.noDup = jd18[, !duplicated(colnames(jd18))] 

# Grow tree 
fit = rpart(Overall.Satisfaction.Index ~ .,
   method="anova", data=short) #method="class" 

printcp(fit) # display the results 
plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits 

# plot tree
plot(fit, uniform=TRUE,
   main="Regression Tree for Satisfaction") 
text(fit, use.n=TRUE, all=TRUE, cex=.8) 

# create attractive postscript plot of tree 
post(fit, file = "./tree.ps",
   title = "Regression Tree for Satisfaction") 
```
